Kinase similarity assessment pipeline for off-target prediction [Article v\versionnumber]

### 2022-06-22 manuscript/manuscript.tex
Fix typo

where $I$ is the identity matrix of the amino acids, and $\SeqA[n]$ the amino acid at position $n$ of the kinase sequence $\SeqA$. Note that not all kinases have residues present at each of the 85 alignment positions. Such gaps are represented by "-" and count as mismatch to any amino acid.

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.5\columnwidth]{sequence_similarity.png}
    \caption{Sequence similarity between EGFR and MET. The $85$- residue pocket sequence is retrieved from KLIFS. The pairwise sequence similarity takes into account the change of the amino acids over evolutionary time.}
    \label{fig:pocket_sequence}
\end{figure}

@@

\subsection{Features of the pipeline}
The developed pipeline contains many useful features. Firstly, it is part of the TeachOpenCADD project~\cite{Sydow_2019_JCheminform, sydow_2022_nar} and extends it with this special kinase edition. Being part of TeachOpenCADD has the following advantages:
\begin{enumerate}
    \item TeachOpenCADD is open-source and freely available at \href{https://github.com/volkamerlab/teachopencadd}{https://github.com/volkamerlab/teachopencadd}, under the Attribution 4.0 International (CC BY 4.0) license.
    \item A dedicated conda package~\cite{conda_forge} facilitates installation.
    \item Online execution is possible via the Binder project \cite{binder_2018}.
    \item The teaching approach makes the notebooks easy to follow.
\end{enumerate}
Moreover, the pipeline is easily adaptable to new sets of kinases as well as new similarity methods, defined by an user.

>>>>

where $I$ is the identity matrix of the amino acids, and $\SeqA[n]$ the amino acid at position $n$ of the kinase sequence $\SeqA$. Note that not all kinases have residues present at each of the $85$ alignment positions. Such gaps are represented by "-" and count as mismatch to any amino acid.

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.5\columnwidth]{sequence_similarity.png}
    \caption{Sequence similarity between EGFR and MET. The $85$-residue pocket sequence is retrieved from KLIFS. The pairwise sequence similarity takes into account the change of the amino acids over evolutionary time.}
    \label{fig:pocket_sequence}
\end{figure}

@@

\subsection{Features of the pipeline}
The developed pipeline contains many useful features. Firstly, it is part of the TeachOpenCADD project~\cite{Sydow_2019_JCheminform, sydow_2022_nar} and extends it with this special kinase edition. Being part of TeachOpenCADD has the following advantages:
\begin{enumerate}
    \item TeachOpenCADD is open-source and freely available at \href{https://github.com/volkamerlab/teachopencadd}{https://github.com/volkamerlab/teachopencadd}, under the Attribution 4.0 International (CC BY 4.0) license.
    \item A dedicated conda package~\cite{conda_forge} facilitates installation.
    \item Online execution is possible via the Binder project \cite{binder_2018}.
    \item The teaching approach makes the notebooks easy to follow.
\end{enumerate}
Moreover, the pipeline is easily adaptable to new sets of kinases as well as new similarity methods, defined by a user.
